---
title: "Cleaning"
author: "Henry Stoddard"
date: "12/30/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
data = load("./Data/NSDUH_full.RData")
```

Recoding to make no = 0 and missing = NA, also combining race categories such that Native American, Alaskan Native, Native Hawaiian/Pacific Islander, Asian, and multiracial all combined into category 4 - "other", Hispanic changed to category 3.
1 = white
2 = black
3 = hispanic
4 = other
```{r}
NSDUH_recode =
  NSDUH_full %>% 
  mutate(MEDMJNEW = recode(MEDMJST2, "2" = 0, "1" = 1),
         newcig = recode(ircigfm, "93" = 0, "91" = 0),
         newalc = recode(iralcfm, "93" = 0, "91" = 0),
         newrace = recode(NEWRACE2, "1" = 1, "2" = 2, "7" = 3, "3" = 4, "4" = 4, "5" = 4, "6" = 4))
```

NOTE: catage is categorical 1 = 12-17, 2=18-25, 3 = 26-34, 4 = 35+ so we will exclude those where catage =1 in later analysis
IRSEX left as is, 1= MALE, 2 = FEMALE


Checking missingness
```{r}
skimr::skim(NSDUH_recode)
```

Dropping old vars and saving new variables as correct type, then saving file for analysis
```{r}
NSDUH_final = 
  NSDUH_recode %>% 
  select(-MEDMJST2, -ircigfm, -iralcfm, -NEWRACE2)

skimr::skim(NSDUH_final)

NSDUH_analysis = 
  NSDUH_final %>% 
  mutate(Year = as.numeric(Year),
         irsex = as.factor(irsex),
         PDEN10 = as.factor(PDEN10),
         MEDMJNEW = as.factor(MEDMJNEW),
         newrace = as.factor(newrace))

save(NSDUH_analysis, file = "./Data/NSDUH_analysis.RData")
write.csv(NSDUH_analysis, file = "NSDUH_analysis.csv")
```

Send to SAS from here for analysis
